---
title: "Sirion Probe Current Proxy"
author: "J. R. Minter"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  knitr:::html_vignette:
    css: theme/jm-mod-vignette.css
    number_sections: yes
    toc: yes
---

```{r, echo=FALSE}
library(png)
library(grid)
library(knitr)
```

# Objective

The objective of this project is to develop a proxy for the measurement
of the probe current on our Sirion FEG-SEM.

# Background

A quality control analysis during the summer of 2016 monitored the
performance of the Oxford detector.

```{r fig.width=7.5, fig.height=5,echo=FALSE,fig.align='center', fig.cap="Performance of the Oxford XMAX detector."}
img <- readPNG("png/Oxford-P4-05eV-2K-ggp.png")
grid.raster(img)
```
Note that the precision of the channel width, zero offset, and resolution
is quite stable. There is, however much more drift in the mean intensity
of the Cu-L peak measured. Scientists at NIST have experienced similar
problems on their FEI Nova NanoSEM. My hypothesis is that there is
current leakage on the connection to the stage connector to the
Faraday cup. The variance is approximately 5%. The uncertainty in the
peak integrals is much lower.

My proposal is to use the X-Ray peak integral from a Si line from small
chips of conductive Si as an internal standard as a proxy for the
probe current.

# The model

I began by simulating the spectrum from Si at the voltages I commonly
use.


```{r fig.width=7.5, fig.height=5.231,echo=FALSE,fig.align='center', fig.cap="Simulation of Si at 100 nA-sec."}
img <- readPNG("png/simulate-Si-voltage-series.png")
grid.raster(img)
```

Next, I simulated 10,000 trajectories for beam voltages between 5
and 30 kV in 1 kV steps, assuming a dose of 100 na-sec dose.


```{r fig.width=7.5, fig.height=5.231,echo=FALSE,fig.align='center', fig.cap="Simulation of Si at 100 nA-sec. Note that the curve is monotonic but non-linear. It is best fit using the LOESS approach."}
img <- readPNG("png/Si-voltage-series-plt-10000.png")
grid.raster(img)
```

I had measured Si at 5 kV (the values are in cts/nA-sec)

```{r, echo=FALSE}
fi <- 'dat/csv/2016-09-07-C-on-Si-5kV-2K.csv'
df.exp <- read.csv(fi, header=TRUE, as.is=TRUE)
kable(df.exp)
```

And my predicted values

```{r, echo=FALSE}
fi <- 'dat/csv/si-loess-pred-10000.csv'
df.calc <- read.csv(fi, header=TRUE, as.is=TRUE)
kable(df.calc[1,])
```

So, at 5 kV, my measured result differs from my calculated result by
a factor of `r round(df.exp[1,3]/df.calc[1,2], 4)`. Note that this was
measured at a 5 mm working distance and the measured *sweet spot* is closer
to 3.5 mm. I have also suspected that we were unable to safely insert 
the detector to a point to achieve the calculated solid angle.

I tried this at 20 kV, again with a home-made Faraday cage:


```{r, echo=FALSE}
fi <- 'dat/csv/2016-09-16-C-on-Si-20kV-2K.csv'
df.exp <- read.csv(fi, header=TRUE, as.is=TRUE)
kable(df.exp)
```

The variance was quite troubling. So I tried the same experiment with
the Ted Pella XCS-8, which has a Cu Faraday cup drilled into the mount.
This was a more consistent calibration.


```{r, echo=FALSE}
fi <- 'dat/csv/2016-09-16-C-on-Cu-20kV-2K.csv'
df.exp <- read.csv(fi, header=TRUE, as.is=TRUE)
mu <- round(mean(df.exp$Cu.Int.mu), 2)
uc <- round(sd(df.exp$Cu.Int.mu), 2)
kable(df.exp)
```

It also looks like we can ignore the C in this case - it was barely
detectable.

We can compute the mean value, `r mu`, the standard deviation, `r uc`,
or on a percentage basis, `r round(100.0*uc/mu, 2)` - about an order of
magnitude better than probe current measurements.

Next, I need to simulate the Cu-L intensity as a function of voltage
for a standard probe current. I can always use Cu tape on individual
specimens...


```{r fig.width=7.5, fig.height=5,echo=FALSE,fig.align='center', fig.cap="Simulation of Cu at 100 nA-sec. Note that the curve is smooth and non-linear. It is best fit using the LOESS approach."}
img <- readPNG("png/Cu-voltage-series-plt-10000.png")
grid.raster(img)
```

