---
title: "Sirion Probe Current Proxy"
author: "J. R. Minter"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  knitr:::html_vignette:
    css: theme/jm-mod-vignette.css
    number_sections: yes
    toc: yes
---

```{r, echo=FALSE}
library(png)
library(grid)
```

# Objective

The objective of this project is to develop a proxy for the measurement
of the probe current on our Sirion FEG-SEM.

# Background

A quality control analysis during the summer of 2016 monitored the
performance of the Oxford detector.

```{r fig.width=7.5, fig.height=5,echo=FALSE,fig.align='center', fig.cap="Performance of the Oxford XMAX detector."}
img <- readPNG("png/Oxford-P4-05eV-2K-ggp.png")
grid.raster(img)
```
Note that the precison of the channel width, zero offset, and resolution
is quite stable. There is, however much more drift in the mean intensity
of the Cu-L peak measured. Scientists at NIST have experienced similar
problems on their FEI Nova NanoSEM. My hypothesis is that there is
current leakage on the connection to the stage connector to the
Faraday cup. The variance is approximately 5%. The uncertainty in the
peak integrals is much lower.

My proposal is to use the X-Ray peak integral from a Si line from small
chips of conductive Si as an internal standard as a proxy for the
probe current.

# The model

I began by simulating the spectrum from Si at the voltages I commonly
use.


```{r fig.width=7.5, fig.height=5.231,echo=FALSE,fig.align='center', fig.cap="Simulation of Si at 100 nA-sec."}
img <- readPNG("png/simulate-Si-voltage-series.png")
grid.raster(img)
```

Next, I simulated 10,000 trajectories for beam voltages between 5
and 30 kV in 1 kV steps, assuming a dose of 100 na-sec dose.


```{r fig.width=7.5, fig.height=5.231,echo=FALSE,fig.align='center', fig.cap="Simulation of Si at 100 nA-sec. Note that the curve is monotonic but non-linear. It is best fit using the LOESS approach."}
img <- readPNG("png/Si-voltage-series-plt-10000.png")
grid.raster(img)
```